---
title: "Toolik Chrlorophyll Concentrations"
author: "Paloma Cartwright"
date: "09/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
library(skimr)
```

## Read in toolik_chlorophyll.csv as a data frame stored as `toolik_cholorphyll`

Use read_csv 
```{r}
toolik_chlorophyll <- read_csv(here::here("data", "data-raw", 
                                           "toolik_chlorophyll.csv"), 
                               na = ".")
```

Explore the imported data with `skimr::skim()`, `names()`, `dim()`, `summary()`

```{r}
skimr::skim(toolik_chlorophyll)
names(toolik_chlorophyll)
dim(toolik_chlorophyll)
summary(toolik_chlorophyll)

```
Overwrite the existing toolik chlorophyll with a new version with lower snake case

```{r}
toolik_chlorophyll <- toolik_chlorophyll %>% clean_names()
```

## Create a scatter plot of depth versus chlorophyll A concentration. 
- make point size `size`  changed based on the concentration 
- Make all the points "cyan4"
- Update the theme to `theme_dark()`

```{r}
toolik_chlorophyll_plot <- ggplot(data = toolik_chlorophyll,
                                  aes(x = active_chl_a_ug_l, y = depth)) +
  geom_point(aes(size = active_chl_a_ug_l, color = depth))

toolik_chlorophyll_plot

```

```{r}
ggsave(here::here("figs", "chlorophyll_graph.jpg"), plot = toolik_chlorophyll_plot)
```

